MSE and dynamic state variable model with sigma function

### 2018-05-14 doc/MSE_MAR_18.tex
pushed changes in tex and code  (for Nekane)
Nekane will split model and plots

Number of vessels                                                    &                       & 700           \\ 
Fuel costs (Euro day\textsuperscript{-1})               &                       & 1240         \\ 
Gear maintenance (Euro day\textsuperscript{-1})  &                       & 0               \\ 
Crew share                                                               &                       & 35\%        \\ 
Landing costs (Euro t\textsuperscript{-1})              &                       & 0               \\
Optimal choice error                                                 & $\sigma $       & 40             \\

@@

\subsection{Management procedure}
\label{sec2.3}
The fisheries model 
The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These manegement strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

>>>>

Number of vessels                                                    &                       & 700           \\ 
Fuel costs (Euro fishing season\textsuperscript{-1})               &                       & 100        \\ 
Gear maintenance (Euro fishing season\textsuperscript{-1})  &                       & 50               \\ 
Crew share                                                               &                       & 35\%        \\ 
Landing costs (Euro t\textsuperscript{-1})              &                       & 0               \\
Optimal choice error                                                 & $\sigma $       & 40             \\

@@

\subsection{Management procedure}
\label{sec2.3}
The fisheries model 
The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These management strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.
